\section{Introduction}

The effects of \elnino{}--Southern Oscilation (ENSO) are now known to be
significant both locally \emph{and} globally.

ENSO has long been known to have powerful effects local to the tropical Pacific
ocean and teleconnected regions: ocean temperatures and atmospheric pressures
vary anomalously high or low, leading to variation in precipitation, cloud
cover, and vegetation cover. ENSO events have been shown to affect storm
activity \citep{wang2002}, and are suggested as a contributing factor in
cyclogenesis \citep{sobel2000}.

\cite{trenberth2012} noted how the strong Russian heat wave, and numerous
other events, were caused by a combination of particularly strong ENSO and
global warming events occuring simultaneously. \cite{bronnimann2007} reviewed
studies relating to the effects of ENSO on European climate and stated ``ENSO is
arguably the most important global climate pattern.'' The review determined that
many Europe-focused studies found clear evidence for ENSO affecting European
climate. Similar studies have appeared with a focus on African climate, with
many again suggesting that ENSO has effects on rainfall \citep{kane2009} and
vegetation \citep{anyamba1996, anyamba2001, anyamba2002}, though in all cases
the climatological response isn't always present or strong.

\vspace{0.5cm}

Modern Africa has been plagued by socioeconomic struggles, with frequent civil
war, little access to education and medicine, and highly unstable
governments. While much progress has been made in recent years\footnote{For more
  information see \url{https://africaindata.org}} the extra stresses of food
shortages and drought may trigger a return to instability.
% TODO Provide actual citation for above. Is the last line here a
% bit... insensitive?
In 2016 the UN Office for the Coordination of Humanitarian Affairs (UNOCHA)
published a report on the response to \elnino{} in East and Southern Africa
\citep{unocha2016}; by their estimates over 19.5 million people and 10.5
children were affected in East Africa alone. As a result of \elnino{} parts of
East Africa received below average rainfall leading to poor harvests and food
shortages. Similarly, parts of Southern Africa experienced the worst drought for
35 years and leading to huge food insecurity. As one of the worst hit countries,
Kenya alone now has over 1.2 million people in a food security crisis.

Malaria has long been a leading cause of death in Africa, particularly in
children, accounting for approximately 18\% of total deaths in children
\citep{IMHE2016}. \citet{Alles1998} states that, at the time of reporting,
malaria transmission intensities---a measure of how effectively malaria is
transmitted in a population---are often two orders of magnitude greater than other
regions where malaria is a significant problem. \citet{loevinsohn1994}
investigated the relationship between climatic warming and malaria incidence
rates in Rwanda, East Africa. The report found that during the particularly warm
period of the late 1980s malaria incidence rates almost doubled, with even
regions previously free of the disease showing an up-take in
incidence.\footnote{Interestingly, the report notes that while there was no
  significant trend in precipitation over the same period, there was heavy rain
  in the years 1987 and 1988 which coincided with a strong ENSO event.}

More recently \cite{craig2004} sought to quantify the association between
various climatic factors---including rainfall and temperature---and malaria
incidence. The report found that \emph{total seasonal cases} of malaria were not
driven by climatological factors; however there was a strong correlation between
interseasonal variability and factors such as the maximum temperatures of the
preceding season.

\vspace{0.5cm}

The importance of weather forecasting cannot be understated. We regularly
consult weather forecasts to inform our clothing choices, to help us decide
whether a family outing should be a trip to the beach or to a museum; should we
bring along an umbrella? is it shirt-and-shorts weather?\footnote{Incidentally
  it is never \emph{shirt-and-\textbf{short}-shorts weather.}} These are
legitimate concerns, but they are decidedly \emph{first-world} concerns. In
parts of the world where the amount of rainfall literally means life or death it
is plainly obvious that forewarning of drought is of paramount importance.
Whereas wealthy nations may import food and water in times of need, much of
sub-Saharan Africa relies on the prosperity of local agriculture to meet dietary
needs. Any negative impact on the harvest -- here we concern ourselves only with
climatological causes -- will severely restrict available food sources
\citep{development2006mapping}.

For this reason, it is imperative that we improve our understand of and ability
to predict this effect in order that we may better prepare and coordinate
responses to prevent humanitarian disasters.

% % Would like to say something here referencing data on drought related
% % deaths in Africa.
% Indeed forewarning of any impending weather is
% important for different reasons depending on the local agriculture:
% forecasting drought allows for stockpiling of water and foods;
% forecasting of inclement weather allows for farmers to prepare for a
% greater yield, and locals to prepare for possible flooding.
% % What other reasons are there for forecasting? This needs rewriting
% % anyway, as it is a bit ugly in terms of wording. Could be more poetic.
% Where discussion of the weather is not ``should I wear a raincoat?''
% but ``will we have enough drinking water?'' weather forecasting should
% be considered a humanitarian imperative. 
% Is there something to say about global warming here? Probably.


%% Local Variables:
%% fill-column: 80
%% TeX-master: "report"
%% End:
